Tables in the project

### 2018-08-09 paper/Chapters/Chapter3.tex
hypertension words added

\subsection{Association between individual level latent classes and hypertension, obesity, and diabetes.}

@@

@@

>>>>

\subsection{Association between individual level latent classes and hypertension, and obesity.}\vspace{-0.3cm}

\subsubsection{Hypertension}\vspace{-0.3cm}

\textbf{Table \ref{tab:tab1hypetension}} presents the characteristics of men and women participants in the NDNS RP 2008/09-15/16 by hypertension status. The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women. Among both sexes, there were significant differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01). Differences were also found for carbohydrate eating patterns defined previously, and total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001). No difference was found among either men or women for geographic location, and ethnicity. Strong evidence of difference was found in women for average household income (32741.5 \textsterling/year in non-hypertensive vs. 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.

@@

	\caption{\label{tab:tab2HYT} ORs (95\%CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults.\\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{Hypertension in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
		\hspace{1em}\hspace{1em}Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
		\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national}}\\
		\multicolumn{6}{l}{{\scriptsize dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}}\\
		\multicolumn{6}{l}{{\scriptsize covariates remained the same with the corresponding Model 1s.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic}}\\ 
		\multicolumn{6}{l}{{\scriptsize regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level}}\\ 
		\multicolumn{6}{l}{{\scriptsize (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never)}}\\
		\multicolumn{6}{l}{{\scriptsize , total energy intake (kJ);}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous),}}\\ 
		\multicolumn{6}{l}{{\scriptsize education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
	\end{tabular}
\end{table}

@@

%
%
%\begin{sidewaystable}
%	\rowcolors{2}{gray!6}{white}
%	
%%	\begin{table}
%		
%		\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults. \\ (NDNS RP 2008/09-2015/16, sample size = 6155)}
%		\centering
%		\fontsize{8}{11}\selectfont
%		\begin{tabular}[t]{lccccccccccc}
%			\hiderowcolors
%			\toprule
%			\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Men (n = 2537)}} & \multicolumn{6}{c}{\textbf{Women (n = 3618)}} \\
%			\cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-12}
%			\textbf{Outcomes} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{Models} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
%			\midrule
%			\showrowcolors
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{Hypertension}}\\
%			\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217 & Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
%			\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
%			\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124 & Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{Hypertension in non-diabetics}}\\
%			\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241 & Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
%			\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
%			\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096 & Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{BMI}}\\
%			\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426 & Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
%			\hspace{1em}Model 1\textsuperscript{\S} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22 & Live with partner\textsuperscript{\P} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{BMI in non-diabetics}}\\
%			\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557 & Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
%			\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269 & Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{WC}}\\
%			\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364 & Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
%			\hspace{1em}Model 1\textsuperscript{**} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103 & Live with partner\textsuperscript{\dag\dag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{WC in non-diabetics}}\\
%			\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606 & Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
%			\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181 & Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
%			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
%			\addlinespace[0.3em]
%			\multicolumn{12}{l}{\textbf{DM}}\\
%			\hspace{1em}Crude model & 1 & 0.39 (0.18, 0.83) & 0.016 & 0.78 (0.43, 1.42) & 0.416 & Crude model & 1 & 0.65 (0.28, 1.47) & 0.296 & 0.38 (0.18, 0.81) & 0.013\\
%			\hspace{1em}Model 1\textsuperscript{\ddag\ddag} & 1 & 0.27 (0.10, 0.73) & 0.012 & 0.78 (0.36, 1.68) & 0.529 & Model 1\textsuperscript{\S\S} & 1 & 1.05 (0.33, 3.35) & 0.928 & 0.52 (0.17, 1.59) & 0.255\\
%			\hspace{1em}Model 2 & 1 & 0.27 (0.10, 0.76) & 0.013 & 0.76 (0.35, 1.65) & 0.493 & Model 2 & 1 & 0.79 (0.25, 2.46) & 0.686 & 0.48 (0.18, 1.32) & 0.155\\
%			\bottomrule
%			\multicolumn{12}{l}{{\scriptsize \textit{Note: }}}\\
%			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
%			\multicolumn{12}{l}{{\scriptsize DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic regression models.}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\P} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{**} Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag\dag} Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag\ddag} Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption,}}\\ 
%			\multicolumn{12}{l}{{\scriptsize TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);}}\\
%			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S\S} Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG.}}\\
%		\end{tabular}
%%	\end{table}
%	
%	\rowcolors{2}{white}{white}
%	
%\end{sidewaystable}

### 2018-08-09 paper/Tables/2by2Table1.Rmd
hypertension words added

>>>>

## Table 2 regressions for hypertension

```{r tab2HYT, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/hypertensionReg.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Model", "Low", "Moderate", "P value[note]", "High", "P value")
dt[2, 1] <- c("Model 1[note]")
# dt[3, 1] <- c("Model 2[note]")
dt[8, 1] <- c("Model 1[note]")
# dt[9, 1] <- c("Model 2[note]")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "ORs (95CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  group_rows("Men (n = 2537)", 1, 6) %>%
  group_rows("Hypertension", 1, 3) %>% 
  group_rows("Hypertension in non-diabetics", 4, 6) %>% 
  group_rows("Women (n = 3618)", 7, 12) %>% 
  group_rows("Hypertension", 7, 9) %>% 
  group_rows("Hypertension in non-diabetics", 10, 12) %>% 
  add_header_above(c(" ", "Carbohydrate eating patterns" = 5)) %>% 
  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national", 
                       "dietary and nutrition survey rolling programme.",
                       "Diabetes was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other", 
                       "covariates remained the same with the corresponding Model 1s.")) %>% 
  add_footnote(c("P values were obtained from wald tests from either linear regression models or logistic regression models.",
                "Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not), BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);", 
                "Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);"),
                notation = "symbol")
```

### 2018-08-09 paper/Tables/2by2Table1.tex
hypertension words added

>>>>

\subsection{Table 2 regressions for
hypertension}\label{table-2-regressions-for-hypertension}

\caption{\label{tab:tab2HYT}ORs (95CI) of carbohydrate eating patterns with hypertension with or without diabetes in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{llllll}
\hiderowcolors
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Carbohydrate eating patterns} \\
\cmidrule(l{2pt}r{2pt}){2-6}
Model & Low & Moderate & P value\textsuperscript{*} & High & P value\\
\midrule
\showrowcolors
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Hypertension}}\\
\hspace{1em}\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217\\
\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227\\
\hspace{1em}\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Hypertension in non-diabetics}}\\
\hspace{1em}\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241\\
\hspace{1em}\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197\\
\hspace{1em}\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Hypertension}}\\
\hspace{1em}\hspace{1em}Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
\hspace{1em}\hspace{1em}Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
\hspace{1em}\hspace{1em}Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Hypertension in non-diabetics}}\\
\hspace{1em}\hspace{1em}Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
\hspace{1em}\hspace{1em}Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
\hspace{1em}\hspace{1em}Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
\bottomrule
\multicolumn{6}{l}{\textit{Note: }}\\
\multicolumn{6}{l}{Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national}\\
\multicolumn{6}{l}{dietary and nutrition survey rolling programme.}\\
\multicolumn{6}{l}{Diabetes was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other}\\
\multicolumn{6}{l}{covariates remained the same with the corresponding Model 1s.}\\
\multicolumn{6}{l}{\textsuperscript{*} P values were obtained from wald tests from either linear regression models or logistic regression models.}\\
\multicolumn{6}{l}{\textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or}\\
\multicolumn{6}{l}{not), BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}\\
\multicolumn{6}{l}{\textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking}\\
\multicolumn{6}{l}{status, total energy intake (kJ), alcohol consumption (g/day);}\\
\end{tabular}
\end{table}
